Community-Conditioned Language Models

### 2020-11-12 paper/paper.tex
idea
use better vocabulary

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2020}
\usepackage[T1]{fontenc}
\usepackage{times}
\usepackage{latexsym}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{pgfplots}
\usepackage{todonotes}
\usepackage{enumitem}
\renewcommand{\UrlFont}{\ttfamily\small}
\usepgfplotslibrary{groupplots}
\pgfplotsset{compat=1.16}

@@

However, we want to measure the ability of the LMCC to correctly
recognize messages coming from a given community $c_j$. We could use
something like an F-score, but we prefer to use the perplexity metric
(again), which is has stronger information-theoretic grounds.
However, this time, the perplexity corresponds to the difficulty of
identifying a community, not predicting a word.
Technically, we consider the average perplexity of the LMCC for a
message coming from community $j$, defined as the exponential of the
entropy of the distribution \(D_j\), which is the (discrete)
probability distribution of predicted community for a random message from
$c_j$. $D_j$ is simply the $j$th row in \(C\). In sum, we have the formula:
\[\Ind_j = e^{-\sum_i C_{ij} log(C_{ij})}\]

We call \(\Ind_j\) the (linguistic) indiscernibility of the community
$c_j$, and it is a measure of how unsure a model is about which
community a message belongs to --- when the message in question is
actually coming from a community $c_j$.

@@

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2020}
\usepackage[T1]{fontenc}
\usepackage{times}
\usepackage{latexsym}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{pgfplots}
\usepackage{todonotes}
\usepackage{enumitem}
\usepackage{cleveref}
\renewcommand{\UrlFont}{\ttfamily\small}
\usepgfplotslibrary{groupplots}
\pgfplotsset{compat=1.16}

@@

However, we want to measure the ability of the LMCC to correctly
recognize messages coming from a given community $c_j$. We could use
something like an F-score, but we prefer to use the entropy metric
which is has stronger information-theoretic grounds, and is a measure
of the difficulty of identifying a community, as estimated by the
model. We call this measure the (linguistic) indiscernibility of the
community $c_j$, and use \(\Ind_j\) to stand for it in formulas.

Technically, it is defined as the exponential of the
entropy of the distribution \(D_j\), which is the (discrete)
probability distribution of predicted community for a random message from
$c_j$. $D_j$ is simply the $j$th row in \(C\). In sum, we have the formula:
\[\Ind_j = e^{-\sum_i C_{ij} log(C_{ij})}\]

@@

\jp{We could also compute the entropy of rows of Cij = snap cosine similarity w/ softmax.}
